New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2022-07-14 paper/paper.tex
reference ggplot2 and ggally

\hypertarget{sec:implementation}{%
\section{Experimenting with new techniques using
Mathematica}\label{sec:implementation}}

@@

\hypertarget{extension-added-in-the-r-package-tourr}{%
\section{\texorpdfstring{Extension added in the R package
\texttt{tourr}}{Extension added in the R package tourr}}\label{extension-added-in-the-r-package-tourr}}

@@

\hypertarget{what-would-be-desirable-for-implementations-in-r}{%
\section{What would be desirable for implementations in
R?}\label{what-would-be-desirable-for-implementations-in-r}}

@@

The authors gratefully acknowledge the support of the Australian
Research Council. The paper was written in \texttt{rmarkdown}
\citep{rmarkdown} using \texttt{knitr} \citep{knitr}.

>>>>

@@

\hypertarget{sec:implementation}{%
\section{Software}\label{sec:implementation}}

\hypertarget{mathematica-notebook}{%
\subsection{Mathematica notebook}\label{mathematica-notebook}}

\hypertarget{extensions-to-the-r-package-tourr}{%
\subsection{\texorpdfstring{Extensions to the R package
\texttt{tourr}}{Extensions to the R package tourr}}\label{extensions-to-the-r-package-tourr}}

@@

Changing slice center

\hypertarget{desirable-interactivity}{%
\subsection{Desirable interactivity}\label{desirable-interactivity}}

@@

The authors gratefully acknowledge the support of the Australian
Research Council. The paper was written in \texttt{rmarkdown}
\citep{rmarkdown} using \texttt{knitr} \citep{knitr}. The scatterplot
matrix of the penguins data was produced by the GGally \citep{GGally}
package built on ggplot2 \citep{ggplot2} graphics.
